Resilience and Home-Space for WSTS \thanks{This work was partly done while the author was supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-08-31 final.tex
section

We now recall the
 undecidable \cite{araki1976PN} decision problem of {\em zero-reachability} in reset-VASS, which consists in, given a
reset-VASS $V=(Q,T)$, and $p(\textbf{u}) \in Q \times \N^d$,
deciding whether $\exists q \in Q ~ p(\textbf{u}) \to^* q(\textbf{0})$.
%
We reduce the zero-reachability problem to the problem of deciding whether a control-transition is live,
which we then reduce to {\sc State-resilience}.
A control-transition $t$ of a reset-VASS is {\em live} in a configuration $r(\textbf{w})$ if for each $q(\textbf{v}) \in \post^*(r(\textbf{w}))$ there exists a 
 $p(\textbf{u})$ with $q(\textbf{v}) \to^* p(\textbf{u})$ such that $t$ is enabled in $p(\textbf{u})$. We say the whole reset-VASS is live if all its control-transitions are
live. This leads to the following problem.

\problemx{$t$-liveness}
{A reset-VASS $V=(Q,T)$, $t \in T$, initial configuration $s_0$}
{Is $t$ live in $s_0$ ? \\}

To better discuss $t$-liveness let us define more formally the upward-closed set of configurations such that $t$ is enabled
$pre(t)=\{ p(\textbf{u}) \in S \mid \exists q(\textbf{v})$ such that $ p(\textbf{u}) \xrightarrow{t} q(\textbf{v}) \}$.

>>>>

We now recall the
 undecidable \cite{araki1976PN} decision problem of {\em zero-reachability} in reset-VASS of dimension $d$, which consists in, given a
reset-VASS $V=(Q,T)$, and $p(\textbf{u}) \in Q \times \N^d$,
deciding whether $\exists q \in Q ~ p(\textbf{u}) \to^* q(\textbf{0})$.
%
We reduce the zero-reachability problem to the problem of deciding whether a control-transition is live,
which we then reduce to {\sc State-resilience}.
A control-transition $t$ of a reset-VASS is {\em live} in a configuration $r(\textbf{w})$ if for each $q(\textbf{v}) \in \post^*(r(\textbf{w}))$ there exists a 
 $p(\textbf{u})$ with $q(\textbf{v}) \to^* p(\textbf{u})$ such that $t$ is enabled in $p(\textbf{u})$. We say the whole reset-VASS is live if all its control-transitions are
live. This leads to the following problem.

\problemx{$t$-liveness}
{A reset-VASS $V=(Q,T)$ of dimension $d$, a transition $t \in T$, an initial configuration $s_0 \in Q \times \N^d$}
{Is $t$ live in $s_0$ ? \\}

To better discuss \alain{flou}$t$-liveness, let us define more formally the upward-closed set of configurations such that $t$ is enabled:
$pre(t)=\{ p(\textbf{u}) \in Q \times \N^d \mid \exists q(\textbf{v})$ such that $ p(\textbf{u}) \xrightarrow{t} q(\textbf{v}) \}$.
